Nested sampling with two objective functions

### 2015-10-31 Paper/ms.tex
Results plot
widths

We tested the algorithm on a simple 100-dimensional example, where the
prior is a uniform distribution between 0 and 1 for each coordinate:
\begin{eqnarray}
\pi(\xx) &=& \prod_{i=1}^{100}
\left\{
\begin{array}{lr}
1, & x_i \in [0, 1]\\
0, & \textnormal{otherwise.}
\end{array}
\right.
\end{eqnarray}
The two objective functions are:
\begin{eqnarray}
L_1(\xx) &=& -\sum_{i=1}^{100} \left(x_i - 0.5\right)^2\\
L_2(\xx) &=& -\sum_{i=1}^{100} \log\left[1 +
\left(\frac{x_i - 0.5}{0.01}\right)^2
\right].
\end{eqnarray}
The canonical distributions at low temperature for $L_1$ and high temperature
for $L_2$ are gaussians centered at 0.5 with standard deviations
XX. At high temperatures for $L_2$ and low temperatures for $L_1$ the
canonical distributions are Cauchy centered at 0.5 with width
YY.

@@

>>>>

We tested the algorithm on a simple 100-dimensional example, where the
prior is a uniform distribution between 0 and 1 for each coordinate:
\begin{eqnarray}
\pi(\xx) &=& \prod_{i=1}^{100}
\left\{
\begin{array}{lr}
1, & x_i \in [0, 1]\\
0, & \textnormal{otherwise.}
\end{array}
\right.
\end{eqnarray}
The two objective functions are:
\begin{eqnarray}
L_1(\xx) &=& -\sum_{i=1}^{100} \left(x_i - 0.5\right)^2\\
L_2(\xx) &=& -\sum_{i=1}^{100} \log\left[1 +
\left(\frac{x_i - 0.5}{0.01}\right)^2
\right].
\end{eqnarray}
The canonical distribution at low temperature for $L_1$ and high temperature
for $L_2$ is a gaussian centered at 0.5 with standard deviation
$\sqrt{T_1/2}$. At high temperatures for $L_2$ and low temperatures for $L_1$ the
canonical distributions are Cauchy centered at 0.5 with width
$0.01\sqrt{T_2}$.

@@

\begin{figure}
\centering
\includegraphics[scale=0.5]{figures/results.pdf}
\caption{Numerical results for the test problem. These compare well with the
true partition function and KL divergence given in Figure~\ref{fig:truth}.
\label{fig:results}}
\end{figure}
